Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-06 doc/manuscript/manuscript.Rmd
add comments
update first paragraph

*Sclerotinia sclerotiorum* (Lib.) de Bary is an ascomycete plant pathogen found worldwide.
This is a necrotrophic pathogen that is primarily homothallic (self-fertilization) [@bolton2006sclerotinia; @sexton2006population].
It has a host range of more than 400 species of plants belonging to 75 families [@boland1994index].
Economically important crops affected by this pathogen include sunflower, soybean, oilseed rape, dry bean, chickpea, peanut, dry pea, lentils and vegetables [@bolton2006sclerotinia]. *Sclerotinia sclerotiorum* causes white mold disease on dry bean (*Phaseolus vulgaris* L.), which can be a yield-limiting in temperate climates [@steadman1983white].

@@

@@

@@

@@

@@

![
Discriminant Analysis on regions showing that Mexico is differentiated from other populations. 
**(a)** Mean population assignment (horizontal axis) probability (vertical axis) for all populations with N > 10 (facets).
Numbers next to source populations indicate population size.
All values sum to one.
**(b)** Scatter plot of first two components from DAPC.
Points represent observed individuals connected to the population centroids with ellipses representing a 66% confidence interval for a normal distribution. 
](../../results/figures/publication/DAPC.pdf){#DAPC width=100%}

>>>>

*Sclerotinia sclerotiorum* (Lib.) de Bary is an ascomycete plant pathogen found worldwide.
This is a necrotrophic pathogen that is primarily homothallic (self-fertilization) [@bolton2006sclerotinia; @sexton2006population] that causes disease on more than 400 plant species belonging to 75 families [@boland1994index].
These include crops of major economic importance such as sunflower (*Helianthus spp.*), soybean (*Glycine max* L.), canola (*Brassica napa* L., *Brassica campestris* L.), and dry bean (*Phaseolus vulgaris* L.) [@bolton2006sclerotinia]. 
On dry bean, *S. sclerotiorum* is the causal agent of White Mold, a devastating disease that can be a yield-limiting in temperate climates [@steadman1983white].

@@

<!-- MCG abundance figure -->

@@

<!-- end figure -->

@@

<!-- MCG graph figure -->

@@

<!-- RDA figure -->

@@

<!-- DAPC figure -->

![
Discriminant Analysis on regions showing that Mexico is differentiated from other populations. 
**(a)** Mean population assignment (horizontal axis) probability (vertical axis) for all populations with N > 10 (facets).
Numbers next to source populations indicate population size.
All values sum to one.
**(b)** Scatter plot of first two components from DAPC.
Points represent observed individuals connected to the population centroids with ellipses representing a 66% confidence interval for a normal distribution. 
The center of each component is represented as grid lines.
](../../results/figures/publication/DAPC.pdf){#DAPC width=100%}

<!-- end figure -->
